---
title: "Using the sdsload package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the sdsload package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(sdsload)
```

## Loading multiple SDS packages

The main function of the sdsload package is to let you load and install all required packages for a number of statistical and data sciences classes at Smith College; this package streamlines the process and ensures all necessary packages are loaded at the beginning of your R session. Let's see how we can accomplish this. First, load the `sdsload` package.

Then, use the `load_sds()` function to load and, if desired, install the packages associated with the SDS classes available in this package. We'll load the introductory SDS class, SDS 100, so we'll pass "sds_100" as the argument. load_sds() then evaluates if the inputted class is available for loading:

```{r}
load_sds("sds_100")
```

The default is to install any uninstalled packages, which is communicated by the built-in install_missing = TRUE argument; the function will do this automatically unless instructed otherwise. Uninstalled packages will not be installed by passing install_missing = FALSE:

```{r}
load_sds("sds_100", install_missing = FALSE)
```

Currently, the available courses in this package are SDS 100, SDS 192, SDS 220, and SDS 291:

```{r}
load_sds("sds_100")
load_sds("sds_192")
load_sds("sds_220")
load_sds("sds_291")
```

If unavailable classes; unquoted arguments; or otherwise funky arguments are passed, load_sds() will message you and inform you of available arguments and their form. For example:

```{r}
try(load_sds(sds_100))
```
returns: 
Error in load_sds(sds_100) : 
Class names must be in quotes.
Correct usage: load_sds("sds_100")
Available classes in this package are: sds_100, sds_192, sds_220, sds_291

## Class Package Data

The sdsload package comes with a data set that stores available Smith College SDS courses and their corresponding packages:

```{r}
sdsload::class_packages
```
